\textbf{NBA Party}

### 2017-07-03 cardinal_analytx_presentation/nightlife_and_sports.tex
Citation for jetlag.

\begin{frame}   \frametitle{Accounting for Jetlag}
  In order to account for jet-lag, we need to be mindful of the direction of travel. We calculate
  \begin{itemize}     \item distance traveled between games,
    \item final direction (bearing) traveling from $a \to b$, and
    \item direction of travel (in east-west degrees) by taking sine.
  \end{itemize}
  Finally, to account for jetlag we interact this east-west measure with travel distance. \end{frame}

@@

\begin{frame}   \frametitle{Analysis: rebounds}
  \begin{itemize}     \item For each player and each game, we calculate the number of rebounds obtained per-minute of gamep-lay
    \item From each observation, we subtract the player's average number of rebounds per minute taken across the entire season.
    \item We then run a linear regression explaining demeaned rebounds as a function of 
      nightlife visitation and other features describing player fatigue.   \end{itemize} \end{frame}

>>>>

\begin{frame}   \frametitle{Accounting for Jetlag}
  Prolonged air travel negatively effects sporting performance.\footnote{Lee and Galvez ('12).}

  In order to account for jet-lag, we need to be mindful of the direction of travel. We calculate
  \begin{itemize}     \item distance traveled between games,
    \item final direction (bearing) traveling from $a \to b$, and
    \item direction of travel (in east-west degrees) by taking sine.
  \end{itemize}
  Finally, to account for jetlag we interact this east-west measure with travel distance.\footnote{Lallensack ('17)} \end{frame}

@@

\begin{frame}   \frametitle{Analysis: rebounds}
  \begin{itemize}     \item For each player and each game, we calculate the number of rebounds obtained per-minute of game-play
    \item From each observation, we subtract the player's average number of rebounds per minute taken across the entire season.
    \item We then run a linear regression explaining demeaned rebounds as a function of 
      nightlife visitation and other features describing player fatigue.   \end{itemize} \end{frame}
